Prognostic and biological relevance of collagen-related genes in prostate cancer

### 2024-02-03 report/markdown/manuscript_supplement.Rmd
95% CI included in Table S16

flextable::flextable(suppl_paper_tbl$model_survival) %>% 
  set_widths(c(3.5, 2.7, 3, 2.8, 2.8)) %>% 
  merge_v(1:2) %>% 
  footnote(1, 1, 
           value = as_paragraph('SVM: Support Vector Machines; GBM: Gradient Boosted Machines.'), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1, 3, 
           value = as_paragraph('pooled GEO: GSE54460, GSE70768, GSE70769, and GSE220095'), 
           part = 'header', 
           ref_symbols = 'b') %>% 
  theme_vanilla

>>>>

flextable::flextable(suppl_paper_tbl$model_survival) %>% 
  set_widths(c(2.8, 2.7, 2.7, 4.6, 2.5)) %>% 
  merge_v(1:2) %>% 
  footnote(1, 1, 
           value = as_paragraph('SVM: Support Vector Machines; GBM: Gradient Boosted Machines.'), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1, 3, 
           value = as_paragraph('pooled GEO: GSE54460, GSE70768, GSE70769, and GSE220095'), 
           part = 'header', 
           ref_symbols = 'b') %>% 
  theme_vanilla
